Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional

### 2025-01-08 paper.tex
add sobol index data in fig/sobol_data

To measure the parameter $x_i$'s contribution to $\tau=\tau(\mathbf{x})$ including all variance caused by its interaction with other parameters $\{x_k, k \neq i \}$, the total Sobol index $S_{T,i}$ is calculated as
%
\begin{equation}
    S_{T,i} = \frac{ \mathbb{E}_{\mathbf{x}_{\sim i}}[ \mathbb{V}_{x_i}(\tau|\mathbf{x}_{\sim i}) ] }{ \mathbb{V}(\tau) } .
    \label{eq:STi}
\end{equation}
%
Here, $\mathbf{x}_{\sim i}$ denotes the vector of all entries of $\mathbf{x}$ but $x_i$. The variance of $\tau$ given a set of $\mathbf{x}_{\sim i}$ taken over $x_i$ is $\mathbb{V}_{x_i}(\tau|\mathbf{x}_{\sim i})$ and $ \mathbb{E}_{\mathbf{x}_{\sim i}}[\cdot]$ denotes the mean of argument $(\cdot)$ taken over all factors but $x_i$. We then consider based on the structure of the vector $\mathbf{x}$ the Sobol index for the reorganization energy as $S_{T,\lambda} = S_{T,1}$, for the site energies as $S_{T,E} = \sum\limits_{i=2}^{N+1} S_{T,i}$, and for the coupling elements as $S_{T,E} = \sum\limits_{i=N+2}^{N+1+N_\text{p}} S_{T,i}$. Using the quasi Monte Carlo method\cite{sobol_global_2001} with a sample size $N_\text{QMC}=1000$ to calculate $S_{T,i}$, we find that $S_{T,\lambda}=0.097$, $S_{T,E} =0.950$ and $S_{T,J}=0.018$. The Sobol indices corroborate the observation from the confidence intervals that the uncertainty in the site energies gives the dominant contribution to the variance of the simulated time-of-flight. Contributions from the reorganization energy and the coupling elements are both small in relation, with the one of $\lambda$ slightly larger than the one of $J$. This is also in line with the general observations on the distributions in Fig.~\ref{fig:mle_MADN_withE}.

>>>>

To measure the parameter $x_i$'s contribution to $\tau=\tau(\mathbf{x})$ including all variance caused by its interaction with other parameters $\{x_k, k \neq i \}$, the total Sobol index $S_{T,i}$ is calculated as
%
\begin{equation}
    S_{T,i} = \frac{ \mathbb{E}_{\mathbf{x}_{\sim i}}[ \mathbb{V}_{x_i}(\tau|\mathbf{x}_{\sim i}) ] }{ \mathbb{V}(\tau) } .
    \label{eq:STi}
\end{equation}
%
Here, $\mathbf{x}_{\sim i}$ denotes the vector of all entries of $\mathbf{x}$ but $x_i$. The variance of $\tau$ given a set of $\mathbf{x}_{\sim i}$ taken over $x_i$ is $\mathbb{V}_{x_i}(\tau|\mathbf{x}_{\sim i})$ and $ \mathbb{E}_{\mathbf{x}_{\sim i}}[\cdot]$ denotes the mean of argument $(\cdot)$ taken over all factors but $x_i$. We then consider based on the structure of the vector $\mathbf{x}$ the Sobol index for the reorganization energy as $S_{T,\lambda} = S_{T,1}$, for the site energies as $S_{T,E} = \sum\limits_{i=2}^{N+1} S_{T,i}$, and for the coupling elements as $S_{T,E} = \sum\limits_{i=N+2}^{N+1+N_\text{p}} S_{T,i}$. Using the quasi Monte Carlo method\cite{sobol_global_2001} with a sample size $N_\text{QMC}=1000$ to calculate $S_{T,i}$, we find that $S_{T,\lambda}=0.097$, $S_{T,E} =0.950$ and $S_{T,J}=0.028$. The Sobol indices corroborate the observation from the confidence intervals that the uncertainty in the site energies gives the dominant contribution to the variance of the simulated time-of-flight. Contributions from the reorganization energy and the coupling elements are both small in relation, with the one of $\lambda$ slightly larger than the one of $J$. This is also in line with the general observations on the distributions in Fig.~\ref{fig:mle_MADN_withE}.
